Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-18 paper/manuscript.tex
text revisions of structure subsection of Results thru paragraph 2

\subsection*{The selected mutations are in the binding footprints for all antibodies}
We visualized for each mutation the fraction surviving selection as a logoplot, and for each site mapped the mutation with the maximum fraction surviving selection onto the HA structure, shown in Figure~\ref{fig:structures}A. 
For all of the antibodies, the sites with mutations exhibiting the greatest fraction escape localize in or near the antibody epitope.
Many amino-acid mutations at most sites can confer escape from the strain-specific antibodies and from S139/1. 
On the other hand, we see selection for only a handful of amino acids at sites of escape from the broad stalk-targeting antibodies.

For S139/1, we observed strong escape mutations at sites 156, 158, and 193, in H3 numbering. 
These three sites surround the receptor-binding pocket, and were previously reported as sites of escape in selection experiments with S139/1~\citep{yoshida2009cross}.
The mutation contributing the greatest fraction of virions surviving selection, G158N, introduces a glycosylation motif (N-X-S/T) at this site.
C179 and FI6v3, which share very similar binding footprints and angles of approach~\citep{dreyfus2013structure}, select for identical escape mutations at several sites (Figure~\ref{fig:structures}B). 
Both antibodies select for the K280S, K280T, and N291S mutations, all of which introduce glycosylation motifs in close proximity to the epitope and all have similar effect sizes in conferring escape from either antibody.

@@

\begin{figure}
\centerline{\includegraphics[width=0.95\textwidth]{figs/logoplots_pymol/logoplots_pymol.pdf}}
\caption{
\label{fig:structures}
{\bf Mutations selected by broad and narrow antibodies.}
(A) The logo plots show the sites where mutations have the largest effect.
Letter heights are proportional to the excess fraction of virions with that mutation that survive antibody, as indicated by the scale bars.
The structures are colored white to red by the excess fraction surviving for the largest-effect mutation at each site, with each antibody scaled separately.  
(B) Sites of selection from anti-stalk antibodies, with the same coloring scale for both antibodies.
(C) Cladogram of HA subtypes, with group 1 in black and group 2 in gray. 
The amino acid at site 38 is indicated. 
Colors indicate whether a subtype is bound or neutralized by C179 if this has been tested.  
}
\end{figure}

>>>>

\subsection*{The selected mutations are near the binding footprints of the antibodies}
Antigenic mutations selected by narrow strain-specific antibodies against HA generally occur at residues in or near the physical binding footprint of the antibody~\citep{yewdell1979antigenic,webster1980determination,caton1982antigenic}.
We examined whether this was also the case for the broad antibodies used in our experiments.
Figure~\ref{fig:structures}A shows a zoomed-in view of the sites of mutations selected by each antibody, as well as their locations on HA's structure. 
It is immediately clear that the selected mutations are nearly all in or near the antibody-binding footprint.

\begin{figure}[h!]
\centerline{\includegraphics[width=0.91\textwidth]{figs/logoplots_pymol/logoplots_pymol.pdf}}
\caption{
\label{fig:structures}
{\bf Mutations selected by broad and narrow antibodies.}
(A) The logo plots show the sites where mutations have the largest effect.
Letter heights are proportional to the excess fraction of virions with that mutation that survive antibody, as indicated by the scale bars.
The structures are colored white to red by the excess fraction surviving for the largest-effect mutation at each site, with each antibody scaled separately.  
(B) Sites of selection from anti-stalk antibodies, with the same coloring scale for both antibodies.
(C) Cladogram of HA subtypes, with group 1 in black and group 2 in gray. 
The amino acid at site 38 is indicated. 
Colors indicate whether a subtype is bound or neutralized by C179 if this has been tested.  
}
\end{figure}

Specifically, for S139/1, we observed strong escape mutations at sites 156, 158, and 193 (Figure~\ref{fig:structures}A; sites are in H3 numbering). 
These three sites surround HA's receptor-binding pocket, and fall directly in the physical binding footprint of the antibody~\citep{lee2012heterosubtypic}.
These are also the same three sites where \citet{yoshida2009cross} selected escape mutants in H1, H2, and H3 HAs. 
Our data show that numerous different amino-acid mutations at each site confer neutralization resistance.
The mutation with the largest effect, D158N, introduces an N-linked glycosylation site.

The mutation contributing the greatest fraction of virions surviving selection, G158N, introduces a glycosylation motif (N-X-S/T) at this site.
C179 and FI6v3, which share very similar binding footprints and angles of approach~\citep{dreyfus2013structure}, select for identical escape mutations at several sites (Figure~\ref{fig:structures}B). 
Both antibodies select for the K280S, K280T, and N291S mutations, all of which introduce glycosylation motifs in close proximity to the epitope and all have similar effect sizes in conferring escape from either antibody.

@@
